Loop Device Performance Overhead for Constraining Batch Job Tasks:\\A Technical Report and Experiment in Metascience

### 2016-05-26 paper.tex
Fixes some typos and formatting in paper Modifies Makefile to make it more efficient

Write performance maintains comparable performance to the native filesystem at a deeper nest level than read performance. However, there is a sharper degradation in performance once a nest depth of four is reached. Similar to the read performance, the user would have to consider the added cost of resource guarantees and constraint if their workflow will execute at higher nest depths.

We note that the metadata micro-benchmark's performance is notably faster for the first four depth levels due to the asynchronous operation of loop devices. This behavior is enabled by default. Since metadata performance is measured by how quickly 10,000 empty files are instantiated, we note this asynchronous batching method is quicker for metadata operations. As is the case with the other two micro-benchmakrs, the metadata performance of a loop device relative to the native filesystem drops off at higher nest levels. In our metadata testing, this drop off occurs at a nest depth of five. Like in the read and write results, the user would have to determine if the slower performance is worth the resource guarantees should their workflow execute at high nest depths.

The results presented in Figure \ref{fig:create} display the median value of each sandbox size's creation time. Like in the throughput performance results, we have provided the median absolute deviation for each sandbox size. We can see a proportional linear increase in creation time as the sandbox size increases which is expected. The smaller sandbox sizes (< 1GB) take very little time to instantiate with 512MB taking approximately six seconds to set up. This small overhead should have minimal impact upon performance except in cases where the task would run in a matter of a few seconds where the overhead for instantiating a loop device could double the duration of a task. Considering larger allocations, we see that the overhead is still quite reasonable. 1GB sandboxes across all three ext filesystems show a creation overhead of approximately eleven seconds. On the high end of our testing spectrum, we see an 8GB allocation having a seventy second instantiation duration. In normal cases, we notice that allocations of 8GB or greater experience computation on the order of tens of minutes or longer, so the creation overhead does not seem to dominate a task's duration. In certain cases, however, only a small fraction of the data passed into the sandbox will be relevant to computation. In this case, the creation overhead may be as great as the time spent on computation. We note that file transfer for the data would dominate a task's duration in this case and not the loop device instantiation.

Loop device deletion seems to be almost trivial in duration. In our implementation, the sandbox is dereferenced once the task is complete. In the future, we may opt to overwrite the disk space consumed by the sandbox with zeros before dereferencing the pointers to the disk, however this was not a priority in the current implementation. In all instances of our deletion overhead testing, we can see that the time taken to remove a loop device is less than half a second. As is expected, the 8GB allocation took the longest to remove. In the lower end of our testing spectrum, we note that the smallest allocations took longer to remove than the mid-range allocation sizes in ext3 and ext4. We posit this may be due to handling within ext3 and ext4 which derefences very small files in a less efficient manner with a neglibgible performance decrease compared to a more advanced handling mechanism for larger files. The largest difference we observe is approximately 0.05 seconds between a 16MB and a 32MB allocation which is a speed no human user would likely notice.

>>>>

Write performance remains comparable to the native filesystem at a deeper nest level than read performance. However, there is a sharper degradation in performance once a nest depth of four is reached. Similar to the read performance, the user would have to consider the added cost of resource guarantees and constraint if their workflow will execute at higher nest depths.

We note that the metadata micro-benchmark's performance is notably faster for the first four depth levels due to the asynchronous operation of loop devices. This behavior is enabled by default. Since metadata performance is measured by how quickly 10,000 empty files are instantiated, we note this asynchronous batching method is quicker for metadata operations. As is the case with the other two micro-benchmarks, the metadata performance of a loop device relative to the native filesystem drops off at higher nest levels. In our metadata testing, this drop off occurs at a nest depth of five. Like in the read and write results, the user would have to determine if the slower performance is worth the resource guarantees should their workflow execute at high nest depths.

The results presented in Figure \ref{fig:create} display the median value of each sandbox size's creation time. Like in the throughput performance results, we have provided the median absolute deviation for each sandbox size. We can see a proportional linear increase in creation time as the sandbox size increases which is expected. The smaller sandbox sizes (less than 1GB) take very little time to instantiate with 512MB taking approximately six seconds to set up. This small overhead should have minimal impact upon performance except in cases where the task would run in a matter of a few seconds where the overhead for instantiating a loop device could double the duration of a task. Considering larger allocations, we see that the overhead is still quite reasonable. 1GB sandboxes across all three ext filesystems show a creation overhead of approximately eleven seconds. On the high end of our testing spectrum, we see an 8GB allocation having a seventy second instantiation duration. In normal cases, we notice that allocations of 8GB or greater experience computation on the order of tens of minutes or longer, so the creation overhead does not seem to dominate a task's duration. In certain cases, however, only a small fraction of the data passed into the sandbox will be relevant to computation. In this case, the creation overhead may be as great as the time spent on computation. We note that file transfer for the data would dominate a task's duration in this case and not the loop device instantiation.

Loop device deletion seems to be almost trivial in duration. In our implementation, the sandbox is dereferenced once the task is complete. In the future, we may opt to overwrite the disk space consumed by the sandbox with zeros before dereferencing the pointers to the disk, however this was not a priority in the current implementation. In all instances of our deletion overhead testing, we can see that the time taken to remove a loop device is less than half a second. As is expected, the 8GB allocation took the longest to remove. In the lower end of our testing spectrum, we note that the smallest allocations took longer to remove than the mid-range allocation sizes in ext3 and ext4. We posit this may be due to handling within ext3 and ext4 which derefences very small files in a less efficient manner with a neglibgible performance decrease compared to a more advanced handling mechanism for larger files. The largest difference we observe is approximately 0.05 seconds between a 16MB and a 32MB allocation which is a slowdown no human user would likely notice.
